Interval Probability for Fuzzy Quantum Theories

### 2016-06-22 prob.tex
prob.tex \subsection{Quantum Interval-valued Probability Measures} Start the third example...
prob.tex \subsection{Quantum Interval-valued Probability Measures} example updates...
prob.tex \subsection{Quantum Interval-valued Probability Measures} Add another example, but not what I really need...

Even if there is a natural map from quantum probability measures to
quantum interval-valued probability measures, there are also some
quantum interval-valued probability measures do not come from quantum
probability measures.

\amr{ The idea will be the following. First describe quantum probability
spaces conventionally. Then talk about the following: 
\begin{itemize}
\item the dimension of the Hilbert space is a parameter that is like the
number of needles; it gives an upper bound on the accuracy of the
numbers that are relevant in expressing probabilities 
\item the intervals will come from two things: the fact that states can
only be prepared to a certain accuracy so when we say the state is
$\ket{\psi}$ we really mean a neighborhood of states close to $\ket{\psi}$ 
\item similarly when we do an experiment with $\proj{\phi}$ we are really
testing a family of projections that are near $\proj{\phi}$; this
fuziness will cause the probability to only be specifiable as intervals 
\end{itemize}
}

>>>>

We have enough examples for quantum interval-valued probability measure,
it is instructive to understand the conditions by studying a measure
which is not a quantum interval-valued probability measure.

\begin{example}[Not three-dimensional quantum interval-valued probability
measure] Given a three dimensional Hilbert space with an orthonormal
basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $. Consider\emph{
$\mathscr{I}=\left\{ \necess,\imposs,\unknown\right\} $}, and $\ket{\ps}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{1})$
as before. Let
\begin{eqnarray*}
\mu(\mathbb{0}) & = & \imposs\textrm{ ,}\\
\mu(\mathbb{1}) & = & \necess\textrm{ ,}\\
\mu(\proj{0}) & = & \necess\textrm{ ,}\\
\mu(\proj{\ps}) & = & \necess\textrm{ ,}\\
\mu(\proj{\psi}) & = & \imposs\textrm{, for }\ip{\psi}{0}=0\textrm{ or }\ip{\psi}{\ps}=0\textrm{ ,}\\
\mu(1-\proj{0}) & = & \imposs\textrm{ ,}\\
\mu(1-\proj{\ps}) & = & \imposs\textrm{ ,}\\
\mu(1-\proj{\psi}) & = & \necess\textrm{, for }\ip{\psi}{0}=0\textrm{ or }\ip{\psi}{\ps}=0\textrm{ ,}\\
\mu(P) & = & \unknown\textrm{, otherwise. }
\end{eqnarray*}
$\mu$ is not a quantum interval-valued probability measure. To verify
this fact, we first consider an orthonormal basis
\begin{eqnarray*}
\ket{\psi_{0}} & = & \frac{1}{\sqrt{2}}\ket{1}+\frac{1}{\sqrt{2}}\ket{2}\\
\ket{\psi_{1}} & = & \frac{1}{\sqrt{3}}\ket{0}-\frac{1}{\sqrt{3}}\ket{1}+\frac{1}{\sqrt{3}}\ket{2}\\
\ket{\psi_{2}} & = & \sqrt{\frac{2}{3}}\ket{0}+\frac{1}{\sqrt{6}}\ket{1}-\frac{1}{\sqrt{6}}\ket{2}
\end{eqnarray*}
However,

\begin{eqnarray*}
 &  & \mu\left(\proj{\psi_{0}}+\proj{\psi_{1}}\right)=\mu\left(1-\proj{\psi_{2}}\right)=\unknown\\
 & \nsubseteq & \imposs+\imposs=\mu\left(\proj{\psi_{1}}\right)+\mu\left(\proj{\psi_{2}}\right)\textrm{ .}
\end{eqnarray*}
\qed\end{example}

\yutsung{For \emph{$\mathscr{I}=\left\{ \necess,\imposs,\unknown\right\} $},
are there any quantum interval-valued probability measures do not
come from quantum probability measures?}
